%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Highlighted Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Job title
	{TVM : Compiler Stack for Deep Learning \Link{https://tvm.ai}} % Organization
	{Jan. 2018 - Dec. 2018} % Date(s)
	{} % Location
	{
		TVM is an end-to-end deep learning compiler stack for CPUs, GPUs and specialized accelerators. I contributed to autotvm package (automated code optimization) and TOPI (tensor operator inventory) package for this project, making it reach parity with the state-of-the-art highly hand-optimized library.
	}

  \cventry
	{} % Job title
	{MAgent : Many-agent Reinforcement Learning Platform \Link{https://github.com/geek-ai/MAgent}} % Organization
	{Jul. 2017 - Dec. 2017} % Date(s)
	{} % Location
	{
		MAgent is a many-agent reinforcement learning platform. It supports efficient training, simulation, and flexible environment design for multi-agent tasks.
	}	


  \cventry
    {} % Job title
    {Malic : x86 Compiler
    	 \Link{https://github.com/merrymercy/compiler2017}	} % Organization
    {May. 2017} % Date(s)
    {} % Location
    {
      Malic is the winner compiler (1/25) with the best performance in Compiler Construction 2017 at ACM Honors Class. It compiles a java-like language into x86-64 asm with basic optimization techniques.
    }

  \cventry
    {} % Job title
    {goGFS: Google File System in golang \Link{https://github.com/merrymercy/goGFS}} % Organization
    {Jul. 2016} % Date(s)
    {} % Location
    {
        goGFS is a simple implementation of the Google File System (GFS) in golang.
        It is tested with a small cluster of inexpensive machines (1 master, 12 chunkservers and 12 clients).
        Fault tolerance is provided.
    }

  \cventry
    {} % Job title
    {VisNBA: Visualize the NBA data \Link{https://github.com/CN-AlbertWu96/Vis\_basketball}} % Organization
    {Mar. 2017} % Date(s)
    {} % Location
    {
        VisNBA is a NBA data visualization tool. It can provide visualizations at game level, player level and team level. Box-score data, SportVU trace data are all supported.
    }


%---------------------------------------------------------
\end{cventries}
