%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
\cventry
	{Ph.D. Student at \Colorhref{https://rise.cs.berkeley.edu/}{RISE Lab}, advised by 
    \Colorhref{https://people.eecs.berkeley.edu/~istoica/}{Ion Stoica} and
    \Colorhref{https://people.eecs.berkeley.edu/~jegonzal/}{Joseph E. Gonzalez}
    } % Job title
	{RISE Lab, University of California, Berkeley} % Organization
	{Sept. 2019 - Present} % Date(s)
	{} % Location
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item{Topic: Machine Learning Systems, Large Language Models}
			\item{Co-founded \Colorhref{https://lmsys.org/}{LMSYS.org}, an organization focused on open-source LLM development, serving as the student leader.}
			\item{Led several impactful LLM projects, including the Vicuna model, Chatbot Arena evaluation platform, and FastChat system.}
			\item{Developed Alpa, a system for automatic large-scale distributed training and serving.}
			\item{Developed Ansor, a framework for generating high-performance tensor programs for deep learning applications.}
		\end{cvitems}
	}


%---------------------------------------------------------
\cventry
	{Research Assistant at \Colorhref{http://sampl.cs.washington.edu/}{SAMPL Lab}, advised by \Colorhref{https://homes.cs.washington.edu/~luisceze/}{Prof. Luis Ceze}} % Job title
	{SAMPL Lab, University of Washington} % Organization
	{Jul. 2018 - Dec. 2018} % Date(s)
	{} % Location
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item{Topic: Compiler for Machine Learning and Machine Learning for Compiler}
			\item{Developed AutoTVM, a machine learning-based auto-tuner for tensor programs.}
			%\item{Achieved state-of-the-art inference performance on a wide range of hardware platforms using AutoTVM.}
		\end{cvitems}
	}

%---------------------------------------------------------

\cventry
    {Research Assistant at \Colorhref{http://apex.sjtu.edu.cn/}{APEX Lab}, advised by \Colorhref{www.wnzhang.net}{Prof. Weinan Zhang} and \Colorhref{http://apex.sjtu.edu.cn/members/yyu}{Prof. Yong Yu}} % Job title
    {APEX Lab, Shanghai Jiao Tong University} % Organization
    {Jul. 2017 - Jun. 2019} % Date(s)
    {} % Location
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item{Topic: Deep Reinforcement Learning and Multi-Agent Systems}
			\item{Developed MAgent, a many-agent reinforcement learning platform.}
			%\item{Implemented deep reinforcement learning algorithms on our platform to demonstrate the emergence of collective intelligence.}
		\end{cvitems}
	}

%---------------------------------------------------------
\end{cventries}
